Compositional equivalences based on Open pNets

### 2020-06-16 2016-Weak-FH-Bisim/WeakBisim.tex
correction page 72-73
Finie ??

\tableofcontents

@@

    \hline
    \end{tabular}
    \bigskip
    That makes a total of 73 WOTs  in the SimpleImpl WOA.

@@

\bigskip
Considering the first triple <b0, 000, True>, we have to prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):

\bigskip
$SS_1 << WI_1$

@@

$SS_3 << WI_3$

\smallskip
$SI_1 << WS_1$

@@

$SI_3 << WS_3$

         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
weak automata, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs from 000 in the implementation automaton.

Preliminary remarks:
  \begin{itemize}
    \item Both pNets trivialy verify the ``non-observability''
      condition: the only vectors having $\tau$ as an action of a
      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct. In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
    \end{itemize}

  \medskip
We will check here 2 of these conditions, starting with the first one: $SS_1 << WI_1$

  $ SS_1 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
    (\texttt{b\_msg}\gets \texttt{m1}, \texttt{b\_ec}\gets 0)}
  {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
  $

@@

@@

@@

  \bigskip
  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:

  $ SI_{4} = \openrule
         {\{\}, True, (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
         {100 \OTarrow {\tau} 210}
         $

  $ WS_4(n) = \openrule
         {\{\}, True, (\texttt{b\_ec}\gets \texttt{b\_ec}+n)}
         {\text{b1} \OTWeakarrow {\tau} \text{b1}}
         \ \forall n\ge 0
         $

  \medskip       A similar reasonning gives us
\begin{itemize}
  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$,
\item and the verification condition\\

         $(\texttt{b\_msg} = \texttt{s\_msg} \land \texttt{b\_ec} = \texttt{s\_ec}) \land True\hspace{3mm} \implies
\exists n.(True \land \tau=\tau \land \\ (\texttt{b\_msg} = \texttt{m\_msg} \land \texttt{b\_ec} = \texttt{m\_ec})  \subst{\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec}}
\uplus \subst{\texttt{b\_ec}\gets \texttt{b\_ec}+n})
$

is easily proved True for $n=0$.
 \end{itemize}

>>>>

% \tableofcontents

@@

    \hline
    \end{tabular}

    \bigskip
    That makes a total of 73 WOTs  in the SimpleImpl WOA.

@@

\bigskip
Consider the first triple <b0, 000, True>, we have to prove the following 6 properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense
of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):

\bigskip
\begin{minipage}{0.2\linewidth} 	 
$SS_1 << WI_1$

@@

$SS_3 << WI_3$
\end{minipage}
\hspace{1cm}
\begin{minipage}{0.4\linewidth}
$SI_1 << WS_1$

@@

$SI_3 << WS_3$
\end{minipage}

\bigskip

         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
weak automata, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
parameterized WOTs) from 000 in the implementation automaton.

We will check here 2 of these conditions.
Preliminary remarks:
  \begin{itemize}
    \item Both pNets trivialy verify the ``non-observability''
      condition: the only vectors having $\tau$ as an action of a
      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the 
transitions (m, msg, ec) are the same, that is not correct. In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting 
variables using suffix 1 for the Specification, and 2 for the Implementation.
    \end{itemize}

  \medskip
Let us start with the first pair: $SS_1 << WI_1$, where:

  $ SS_1 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-a1}\}, 
 [\forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)} ], ()}
  {\text{b0} \OTarrow {\nounderline{\texttt{p-a1}}} \text{b0}}
  $

$ WI_1 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-a2}\}, 
 [\forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)} ], ()}
{000 \OTWeakarrow {\texttt{p-a2}} 000}$

@@

\begin{itemize}
  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
  \item Triple ($\text{b0},  000,  True$) is in $\mathcal{R}$.
  \item The verification condition \\
    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
   \left[\exists fv_{OT_x}.
  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$

@@

$\forall \texttt{p-a1}. \{True \land \forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)}\\
 \hspace{3mm} \implies \exists \texttt{pa-2}. 
(\texttt{p-a1} = \texttt{p-a2}
\land \forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)}
\land \nounderline{\texttt{p-a1}} = \nounderline{\texttt{p-a2}} 
\land True\}$

\medskip That is trivialy true, choosing pa-2 = pa-1 for each p-a1.

@@

  \bigskip
  All others pairs from this set are just as trivialy prove true.
